Curation of NYC 311 Request Open Data

### 2023-06-01 talk/slides.Rmd
wrapped long lines

## Invalid Data: Created/Closed Date
```{r date}
t1 <- strptime(d311$closed_date, format = '%m/%d/%Y %I:%M:%S %p')
t0 <- strptime(d311$created_date, format = '%m/%d/%Y %I:%M:%S %p')
tt <- as.numeric(difftime(t1, t0, units =  "secs"))

badTime <- subset(d311, tt <= 0, select = c("created_date", "closed_date", "agency"))
nrow(badTime)
sum(tt == 0, na.rm = TRUE)
summary(tt[tt < 0 & (!is.na(tt))])
table(badTime$agency)
```

@@

## Invalid Data: Borough
```{r borough}
validBorough <- c("BRONX", "BROOKLYN", "MANHATTAN", "QUEENS", "STATEN ISLAND")
badBorough <- subset(d311, ! borough %in% validBorough,
                     select = c("borough", "agency"))
head(table(badBorough$agency))

validBB <- c("1", "2", "3", "4", "5")
badBB <- subset(d311, ! borough_boundaries %in% validBB,
                select = c("borough_boundaries", "agency"))
head(table(badBB$agency))

@@

## Invalid Data: Police Precincts

```{r nypd}
validPolice_precincts <- scan("../data/NYPDPrecincts2023.csv", skip = 1)
badPolice_precincts <- subset(d311, ! police_precincts %in% validPolice_precincts,
                              select = c("police_precincts", "agency"))
sort(table(badPolice_precincts$agency), decreasing = TRUE)
```

>>>>

## Invalid Data: Created/Closed Date
```{r date}
t1 <- strptime(d311$closed_date, format = '%m/%d/%Y %I:%M:%S %p')
t0 <- strptime(d311$created_date, format = '%m/%d/%Y %I:%M:%S %p')
tt <- as.numeric(difftime(t1, t0, units =  "secs"))
badTime <- subset(d311, tt <= 0,
                  select = c("created_date", "closed_date", "agency"))
nrow(badTime)
sum(tt == 0, na.rm = TRUE)
summary(tt[tt < 0 & (!is.na(tt))])
table(badTime$agency)
```

@@

## Invalid Data: Borough
```{r borough}
validBorough <- c("BRONX", "BROOKLYN", "MANHATTAN", "QUEENS", "STATEN ISLAND")
badBorough <- subset(d311, ! borough %in% validBorough,
                     select = c("borough", "agency"))
head(table(badBorough$agency))
```

## Invalid Data: Borough_boundaries and Park_borough
```{r borough2}
validBB <- c("1", "2", "3", "4", "5")
badBB <- subset(d311, ! borough_boundaries %in% validBB,
                select = c("borough_boundaries", "agency"))
head(table(badBB$agency))

@@

## Invalid Data: Police Precincts
```{r nypd}
validPolice_precincts <- scan("../data/NYPDPrecincts2023.csv", skip = 1)
badPolice_precincts <- subset(
    d311, ! police_precincts %in% validPolice_precincts,
    select = c("police_precincts", "agency"))
sort(table(badPolice_precincts$agency), decreasing = TRUE)
```
